### 2018-03-27 document/ms.tex
First commit of the manuscript draft

%\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
%\documentclass[12pt,preprint]{aastex}

%\usepackage{lineno}
%\usepackage{blindtext}
%\linenumbers

\let\pwiflocal=\iffalse \let\pwifjournal=\iffalse
%From: http://arxiv.org/format/1512.00483
%\input{setup}
\input{mgs_setup}

\newcommand{\iancze}{{\sc C15}}

\providecommand{\eprint}[1]{\href{http://arxiv.org/abs/#1}{#1}}
\providecommand{\adsurl}[1]{\href{#1}{ADS}}
\newcommand{\name}{LkCa 4 }
\newcommand{\project}[1]{\textsl{#1}}
%\def\vsini{$v\sin{i_*}$}

\slugcomment{In preparation}

\shorttitle{Physical properties of spotted Taurus members}

\shortauthors{Gully-Santiago et al.}

\bibliographystyle{yahapj}

\begin{document}

\title{The coverage fraction of starspots on young Taurus members and consequences for stellar ages estimates at 1$-$10 Myr}

\author{Michael A. Gully-Santiago,\altaffilmark{1}, author list TBD}

\altaffiltext{1}{Kepler/K2 Guest Observer Office, NASA Ames Research Center, Moffett Field, CA, USA}

\begin{abstract}

We assess starspot temperatures and coverage fraction for three heavily spotted Taurus pre-main sequence young stellar objects from their high-resolution, high bandwidth near infrared IGRINS spectroscopy.  We forward model the spectra with a mixture of cool and hot photosphere components using the \texttt{Starfish} spectral inference framework.  The disk-free, non-accreting sample members have 10$-$30 years worth of polychomatic photometry, which we use in four ways: first, to register the acquisition time of the spectroscopic measurement to the stellar rotational phase; second, to derive the secular changes of areal coverage fraction over 1 to 30 year timescales; third, to derive rotation periods; and fourth, to assign lower-limits to areal filling factors based on the amplitude of photometric variation and limiting case of non-emitting equatorial spots.  We derive starspot temperatures in the range of $x$ to $y$ K, and filling factors of $v$ to $z$.  These filling factors are typically $k$ to $m$ times higher than the limiting case of non-emitting equatorial spots, implying that either the stars possess large circumpolar starspots with the stellar spin axis inclined moderately towards our reference frame, or that the stars possess three or more dominant temperature components, rendering our two-temperature retrieval process flawed.  The filling factors and temperatures cause effective temperature estimates to systematically decrease, confounding age and mass estimates of these young stars and by extension all previous spectral-type-based estimates of fundamental properties of heavily spotted stars, though more work is needed.  The observations of secularly varying photometric amplitudes are consistent with the physical interpretations that some or all young stars pass through short-lived phases of enhanced starspot coverage, or that starspots migrate from near the poles towards the equator over time.

\end{abstract}

\keywords{stars: fundamental parameters ---  stars: low-mass --- stars: statistics}

\maketitle

\section{Introduction}\label{sec:intro}

Wow, starspots are everywhere, look at this paper from Brett Morris \citep{}.

\section{Observations}\label{sec:obs}

\subsection{IGRINS Spectroscopy}\label{sec:igrins}
Here are some citations:

IGRINS \citep{park14}

The data were reduced with the Pipeline Package \citep{jaejoonlee15}.

\subsection{Photometric monitoring}

We used photometry from \citep{grankin08}.

ASAS3 \citep{pojmanski04}?

Integral-OMC \citep{garzon12}?

The AAVSO archive \citep{kafka16}?

Unpublished data from the ASAS-SN survey \citep{shappee14}, yes!

Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.

2MASS \citep{skrutskie06}.

\section{FITS TO HIGH RESOLUTION SPECTRA}\label{sec:Starfish}

\subsection{Methodology}\label{sec:methods}

Of course we need! \citet[hereafter \iancze]{czekala15}
yay!

Phoenix woo!: \citep{husser13}.

Somers woo!: \citep{somers15}.

We use \texttt{emcee} \citep{foreman13}.

\section{Conclusions}

Yay, we did it!

\clearpage
\pagebreak

\appendix

\section{Are starspots confusing?}
\label{methods-details}

Short answer: no!

\acknowledgements

We thank ADS!

{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}, \facility{Gaia}

{\it Software: }
 \project{pandas} \citep{mckinney10},
 \project{emcee} \citep{foreman13},
 \project{matplotlib} \citep{hunter07},
 \project{numpy} \citep{vanderwalt11},
 \project{scipy} \citep{jones01},
 \project{ipython} \citep{perez07},
 \project{gatspy} \citep{JakeVanderplas2015},
 \project{starfish} \citep{czekala15},
 \project{seaborn} \citep{waskom14}
%\software{%
% \project{pandas} \citep{mckinney10}
%    \project{emcee} \citep{foreman13},
% \project{matplotlib} \citep{hunter07},
% \project{numpy} \citep{vanderwalt11},
% \project{scipy} \citep{jones01},
% \project{ipython} \citep{perez07},
% \project{gatspy} \citep{JakeVanderplas2015},
% \project{starfish} \citep{czekala15}}.

\clearpage

\bibliographystyle{apj}
\bibliography{ms}

\end{document}

### 2018-03-27 document/ms.tex
Worked on the paper at the Palo Alto library which is a nice library.

@@
 
-\shorttitle{Physical properties of spotted Taurus members}
+\shorttitle{Extreme Starspots in Taurus}
 
@@
 
-Wow, starspots are everywhere, look at this paper from Brett Morris \citep{}.
+The evolutionary state of a star can be superbly predicted with an age and a mass.
+Angular momentum and metallicity further improve those predictions.
+Unfortunately the age of a star cannot be trivially measured.
+Pre-main sequence isochronal methods provide only coarse estimates of cluster ages, with perhaps 100\% uncertainties attributable to both intrinsic scatter and systematic bias.
+Isochronal models generally ignore angular momentum, a safe bet after stars have resided on the pre-main-sequence for much longer than their formation timescale.
+Pre-main sequence stars differ.
+For the first $1-100$ Myr of a star's life, the rotation rate of a star may inhibit convective efficiency, making the star dwell in its puffed-up, larger-than-expected radius, in order to allow the same amount of internal energy to escape.
+The extra-high rotation rates of young stars interplay with both global and surface magnetic fields and environmental factors to yield complex evolutionary phenomena.
+
+One observational manifestation of rotationally-heightened magnetic fields is the presence of \emph{starspots}.
+Starspots serve as a familiar---albeit inexact---avenue through which we can quantify possible limitations to isochronal age estimates.
+Importantly, starspots possess many favorable observational properties that form the central thrust of this paper.
+In our previous paper \citep{2017ApJ...836..200G}, we combined multiple datasets to reveal a large $\sim75\%$ coverage fraction of starspots on the surface of the Weak-Lined T-Tauri Star (WTTS) LkCa~4.
+Here we seek to identify whether LkCa~4 merely represents an extreme outlier, or whether other WTTS's can possess similiarly large starspots.
+
+We first emphasize possible geometric degeneracies that can give rise to larger-than-expected starspots.
+We then collate numerous photometric and spectroscopic data sources (Section XXX), and their starspot-centric analyses (Section XXX).
+We combine inferences on our small sample of stars to assess the effect of starspots on the pre-main sequence HR-diagram (Section XXX).
+Finally we question our initial assumptions in Section XXX.
 
@@
 \subsection{IGRINS Spectroscopy}\label{sec:igrins}
+
+Recently, \citet{2017ApJ...836..200G} found evidence for a large starspots on the Weak-Lined T-Tauri Star LkCa 4.
 Here are some citations:

### 2018-07-13 document/ms.tex
Uncomitted updates to the manuscript

@@
 
+%Fill in more thereoy here
+\citet{somers15} emphasized the roll of starspots in inferring stellar ages.
+
 We first emphasize possible geometric degeneracies that can give rise to larger-than-expected starspots.
@@
 
-Recently, \citet{2017ApJ...836..200G} found evidence for a large starspots on the Weak-Lined T-Tauri Star LkCa 4.
-Here are some citations:
-
-IGRINS \citep{park14}
-
+V827 Tau was observed on the Immersion Grating Infrared Spectrograph \citep[IGRINS]{park14} at the 2.7~m Harlan J.
+Smith Telescope at McDonald Observatory on 2014-11-21 at 05:23 UTC by observers SK Park, H Kim, JJ Lee.
 The data were reduced with the Pipeline Package \citep{jaejoonlee15}.
@@
 
-We used photometry from \citep{grankin08}.
+We compiled many sources of publicly available $V-$band photometry datapoints including 236 from \citep{grankin08}, 552 from ASAS3 \citep{pojmanski04}, 473 from the AAVSO archive \citep{kafka16}, and 306 unpublished data points from the ASAS-SN survey \citep{shappee14}.
+We spot-checked the diverse sources of photometry finding consistency in estimated flux levels when acquired near-contemporaneously.Figure \ref{fig:PhotTime} shows the compilation of all available photometry on V827 Tau.
+Figure \ref{fig:PhotStamps} shows a zoom-in postage stamp on each season, phase folded with a period $P=3.75837$ days.
 
-ASAS3 \citep{pojmanski04}?
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth]{figures/V827_phot1990-2017.pdf}
+ \caption{Compilation of archival and new flux measurements in $V-$band for V827 Tau, normalized to the global maximum flux value, which occurred in 1990.
+The y-axis equals the minimum starspot area, when flux deficits are interpreted with the simplest possible analytic starspot model.}
+ \label{fig:PhotTime}
+\end{figure*}
 
-Integral-OMC \citep{garzon12}?
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth]{figures/V827Tau_25season_stamps_V.pdf}
+ \caption{Phase-folded $V-$band flux measurements of V827 Tau grouped into 25 observing seasons, and normalized to the global maximum in 1990.
+The y-axis equals the minimum starspot area, when flux deficits are interpreted with the simplest possible analytic starspot model.}
+ \label{fig:PhotStamps}
+\end{figure*}
 
-The AAVSO archive \citep{kafka16}?
+We retrieved K2 Campaign 13 (C13) \cite{2014PASP..126..398H} lightcurves for V827 Tau, possessing EPIC ID 210698281.
 
-Unpublished data from the ASAS-SN survey \citep{shappee14}, yes!
+%We retrieved 2MASS photometry \citep{skrutskie06}.
 
-Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.
+\section{Analysis}\label{sec:Analysis}
+%Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and Fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.
+ We performed a multiterm Lomb-Scargle periodogram \citep{ivezic14}, and Fourier series truncated to the first $\sim 4$ components \citep{vanderplas15a} on the K2 C13 lightcurve, yielding a 3.7584 day period.
+We then fit a second order polynomial plus sine-and-cosine model with linear least squares.
+The periodic minimum K2 flux corresponds to a flux decrement of 23.5\% from its maximum.
+Figure \ref{fig:V827TauK2} shows the lightcurve overplotted with the sinusoidal model.
 
-2MASS \citep{skrutskie06}.
+ \begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth]{figures/V827_Tau_K2C13_lightcurve.pdf}
+ \caption{K2 C13 lightcurve of V827 Tau with a polynomial and sinusoidal model overplotted.  A few flares are perceptible.}
+ \label{fig:V827TauK2}
+\end{figure*}
 
-\section{FITS TO HIGH RESOLUTION SPECTRA}\label{sec:Starfish}
+We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra using the inference framework \texttt{Starfish} \citep{czekala15}, as extended by \citet{2017ApJ...836..200G}.
+We employed PHOENIX synthetic model with an updated version of \texttt{Starfish} that maintains the native absolute fluxes from \citet{husser13}, rather than the slightly inaccurate interpolation introduced in the Appendix of \citet{2017ApJ...836..200G}.
+We ran 5000 samples with 40 \texttt{emcee} walkers \citep{foreman13}, with manual spot-checking of convergence.
+We find typical filling factors around $f_\mathrm{spot} \sim 75\%$ and temperatures $T_\mathrm{spot} \sim 2600$ K.
 
-\subsection{Methodology}\label{sec:methods}
+We observed reasonably good agreedment when we overplotted our model prediction spectra with the data.
+We do not expect the models to be perfect, due to known model mis-specifications such as imperfect line lists and un-modeled magnetic Zeeman broadening, to name a few.
 
-Of course we need! \citet[hereafter \iancze]{czekala15}
-yay!
+The archival and K2 lightcurves constrain the minimum possible starspot coverage, assuming the Simplest Possible Analytic Starspot Model (SPASM).
+Briefly, the SPASM interprets the lightcurve minimum as arising from a single, non-emitting, equatorial starspot on an edge-on star, and interprets the lightcurve maximum as \emph{spot-free}, that is, entirely devoid of starspots.
+With these admittedly extreme assumptions, the flux minimum $F_{min}$ is exactly equal to the starspot areal surface coverage fraction, $f_{\mathrm{spot}}$.
+The SPASM can be applied to a single season, such that there always exists a spot-free hemisphere, or can be applied to a global, long-term photometric dataset such as the one we have assembled for V827 Tau.
+The global maximum flux for V827 Tau occurred on September 21, 1990, with $V=12.242$.Since then, the flux has faded 40\% to a median $V-$band magnitude of 12.63 in the 2016-2017 season.
+The IGRINS spectrum was coincidentally acquired at the minimum of the rotationally modulated flux lightcurve, which corresponds to a global $F_{min} = f_{\mathrm{spot, min}} = 50\%$.
 
-Phoenix woo!: \citep{husser13}.
+Figure \ref{} plots the constraints of starspot filling factor versus starspot temperature.
+The burned-in MCMC draws from the posterior probability density distribution inferred from IGRINS spectra aggregated for all spectral orders are overplotted as a 2D-histogram.
 
-Somers woo!: \citep{somers15}.
-
-We use \texttt{emcee} \citep{foreman13}.
+ \begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth]{figures/V827_Tau_Starfish_results.pdf}
+ \caption{Results of Starfish-based inference of starspot filling factor and temperature for 22 IGRINS $H-$band orders.
+The size of the points is proportional to the strength of the posterior constraint on $f_{\rm spot}$ for each order.}
+ \label{fig:V827TauStarfish}
+\end{figure*}
 
@@
 
-Yay, we did it!
+Reiteration here.
 
@@
 
+%ADS
 We thank ADS!
+
+%Kepler
+This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.
+
+% MAST
+Some/all of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
 

### 2018-07-13 code/plot_specific_mix_model.py
updates to metadata, plotting code for V827 Tau

@@ -336,6 +336,8 @@ if args.static:
     # Sort the flatchain by fill factor:
     fc_sorted = fc
     ind_med = 60 #Random
+    ind_lo = 6 #0.05*8000
+    ind_hi = 114 #0.95*8000
 
     df_out = pd.DataFrame({'wl':wl, 'data':data})
 

### 2018-07-13 code/xphotometryx.py

@@ -383,7 +383,7 @@ def plot_season_minimum(master, season_agg, epochs, ylim=(0, 1.1), savefig_file=
 
 
         # plot the phased data
-        ax = fig.add_subplot(6,4,1 + i)
+        ax = fig.add_subplot(6,5,1 + i)
         plt.plot(tfit/this_P, yfitV, alpha=0.5)
         ax.errorbar(phased_t, y, dy, fmt='.k', ecolor='gray',
                     lw=1, ms=4, capsize=1.5)
@@ -433,6 +433,12 @@ def flatten_photometry():
         if fn_df.ASAS3_fn[i] is not np.NaN:
             as3 = flat_ASAS3('../data/ASAS3/'+fn_df.ASAS3_fn[i])
             df_list.append(as3)
+        if fn_df.AAVSO_fn[i] is not np.NaN:
+            aavso = flat_AAVSO('../data/AAVSO/'+fn_df.AAVSO_fn[i])
+            df_list.append(aavso)
+        if fn_df.IOMC_fn[i] is not np.NaN:
+            IOMC = flat_IOMC('../data/Integral_OMC/'+fn_df.IOMC_fn[i])
+            df_list.append(IOMC)
         master = pd.concat(df_list, join='outer', ignore_index=True, axis=0)
         master['year'], master['month'], master['day'] = jd_to_date(master.JD_like.values)
         master = assign_season(master)
@@ -462,8 +468,8 @@ def master_photometry():
         master = master.append(this_master, ignore_index=True)
 
     #Add a row for flux
-    master['flux_rel'] = 10**(-1.0*master.Vmag/2.5)
-    master['flux_rel'] = master['flux_rel'] /np.percentile(master.V_flux_rel, [99])
+    #master['flux_rel'] = 10**(-1.0*master.Vmag/2.5)
+    #master['flux_rel'] = master['flux_rel'] /np.percentile(master.V_flux_rel, [99])
 
     return master
 

### 2018-09-13 document/ms.tex
Add prose to the paper on methods for interpreting lightcurves

@@
 Finally we question our initial assumptions in Section XXX.
+
+\section{Methods}\label{sec:methods}
+
+\textbf{Our limited understanding of starspot properties, observational biases (ref `Table A1`)}
+Observational limitations usually preclude a complete accounting of a star's surface structures.
+In this section we consider a range of extreme limiting cases of starspot geometries as a guide to interpreting observations.
+These admittedly pathological limiting cases do not represent physically plausible scenarios.
+Instead they serve as benchmarks beyond which no further physical models can exist without changing assumptions or dismissing observations.
+
+In this paper we will assume the target stars are all \emph{starspot dominated}, meaning that in the observations of interest, the dominant variance attributable to stellar activity arises from the presence of darker-than-average regions with characteristic temperatures cooler than their ambient photospheres, and not from brighter-and-hotter-than-average regions such as faculae or plages.
+It is not yet known in which scenarios this assumption holds, but early evidence suggests that rapidly rotating sun-like stars are more likely to be starspot dominated than plage dominated in the visible waveband \citep{2017ApJ...851..116M}.
+Tomographic maps of rapidly rotating young stars also indicate starspot domination \citep{donati14}.
+While most results of the paper work equally well by swapping faculae-dominated for starspot-dominated, the assumptions utterly fail if we allow starspots and faculae to have comparable effect sizes on the same target star.
+
+This paper focuses on methodologies applicable to disk-free, accretion-free rotating young stars, which serve as a great testbed for understanding starspots owing to their large surface magnetic fields and large amplitude of photometric variability.
+The methods should also apply to main sequence and post-main sequence stars, albeit at typically diminished effect sizes.
+
+\subsection{Limiting cases for interpreting monochromatic lightcurves}
+The appearance and disappearance of starspots onto the unresolved hemisphere of a rotating star results in familiar rotationally-modulated stellar lightcurves.
+Monochromatic lightcurves cannot be inverted unambiguously to yield a mapping of surface structures.
+Young stellar lightcurves rarely show flat-topped lightcurves indicative of a single starspot.
+Instead, most Kepler/K2 lightcurves of disk-free, accretion-free rotating young stars look like sine waves, or mixtures of sine waves.
+The sine wave periods offer a simple interpretation-- the rotation period of the star if solid body rotation is assumed, or the rotation period evaluated at the latitude of the dominant starspot group in the case of differential rotation.
+The sine wave amplitudes encode partial information about the starspot \emph{size} and temperature contrast to the ambient photosphere.
+Unambiguously interpreting the absolute starspot \emph{size} and temperature from monochromatic lightcurve amplitudes requires additional geometric assumptions on the number, size, lifetimes, latitudinal and longitudinal distributions, and clustering properties of spots.
+Observations of these quantities exists only for the sun, so their adoption lacks justification in anything but solar analogs.
+Figure \ref{fig:cartoon} illustrates four examples of disparate stellar surface morphologies that possess comparable or identical photometric amplitudes and periods.
+
+The first scenario illustrates a solitary non-emitting (i.e.
+zero Kelvin) starspot near the equator of a modestly inclined star.
+Ignoring limb darkening, the peak-normalized, peak-to-valley amplitude of of the lightcurve is equal to the areal filling factor of the starspot.
+
+The second scenario illustrates is pathological, but informative.
+Consider an equator-on star in which one entire hemisphere (e.g.
+Eastern Hemisphere) possesses an isothermal photosphere, and the diametrically opposed hemisphere (e.g.
+Western Hemisphere) possess a cooler isothermal temperature.
+The cooler hemisphere represents the lightcurve minimum, in which the observer receives less band-averaged flux simply because $T^4$ is smaller.
+No known physical process is capable of delivering such a pathological structure, but nevertheless the temperature difference between the two hemispheres represents the minimum possible temperature contrast of a starspot, assuming the spots are isothermal.
+The peak-normalized, peak-to-valley amplitude of of the lightcurve is equal to:
+
+\begin{equation}
+1- \int \frac{f_{\rm cool}(\lambda)}{f_{\rm ambient}(\lambda)} \epsilon(\lambda) d\lambda
+\end{equation}
+
+where $f_{\rm cool}$ and $f_{\rm ambient}$ refer to the flux of the photospheres for the cooler and hotter hemispheres respectively, and the integration includes the wavelength-dependent instrumental response.
+
+The third illustration depicts another pathological geometry: the \emph{pole-on} star has a starspot that grows and shrinks cyclicly with a period $P \neq P_{\rm rot}$.
+In this scenario, the rotation period is likely to be mis-identified.
+The lightcurve amplitude depends on the size and temperature contrast of the spot.
+
+The right-most illustration depicts a high-latitude active longitude in which the starspot is always visible from the observers perspective, but rotational modulation geometrically forshortens the perceived solid angle of the spot owing to projection effects, and limb darkening.
+The amplitude of the lightcurve depends sensitively on the inclination of the star, the latitude of the spot, the wavelength-dependent limb darkening, the waveband of the observation, the temperature constrast of the spot, and the size of the spot.
+
+\begin{figure*}
+ \centering
+ \includegraphics[width=0.98\textwidth, trim={0 5cm 0 4cm},clip]{figures/cartoon_illustration.pdf}
+ \caption{Cartoon illustration of stars possessing different inclinations, starspot geometries, and positions, yet possessing the same lightcurve morphologies.}
+ \label{fig:cartoon}
+\end{figure*}
 

### 2018-09-15 document/ms.tex
Add more prose-- practical lightcurve considerations.  Tick off some outline tasks.

@@
 %\linenumbers
+%\usepackage{breqn}
+\usepackage{amsmath}
 
@@
 
-\textbf{Our limited understanding of starspot properties, observational biases (ref `Table A1`)}
+\textbf{Our limited understanding of starspot properties, observational biases}
 Observational limitations usually preclude a complete accounting of a star's surface structures.
@@
 
-The second scenario illustrates is pathological, but informative.
+The second scenario is pathological, but informative.
 Consider an equator-on star in which one entire hemisphere (e.g.
@@
 
+\subsection{Practical considerations for monochromatic lightcurves}
+
+Deriving amplitudes from sinusoidal lightcurves should be as simple as measuring the peak-minus-valley flux differences.
+In practice, additional factors complicate such a straightforward analysis.
+One main uncertainty is how to treat \emph{secular} trends, in which the star's flux waxes and wanes with both an oscillatory function of periods $P_{\rm rot}$ and with a slow-varying mean level with characteristic timescales $t_{\rm secular}$.
+Secular changes in flux could be interpreted as a growing or waning average starspot coverage fraction as in a long-term stellar activity cycles.
+The interpretation of secular trends depends on to-what-extent instrumental artifacts mimic these time-series structures.
+In Kepler/K2, for example, spurious secular trends can exist at the few percent level as point spread functions leak out of pre-defined aperture masks due to spacecraft-induced image motion, thermal effects, and other instrumental systematic effects.
+Increasing aperture size can sometimes, partially mitigate these biases at the expense of greater variance and read noise.
+The characteristic timescales of these instrumental biases tend to resemble the observing season- either campaigns for K2, or quarters for Kepler prime.
+Disk-free young stars exhibit bona fide secular trends of up to half a magnitude over periods of years-decades based on decades of ground-based photometric monitoring \citep{grankin08}.
+
+In this paper we propose a practical compromise.
+We determine peak-normalized, peak-to-valley sinuoidal amplitudes at the rotation timescale from high-precision space-based time-series observations, conservatively deeming any secular trends as spurious.
+We additionally determine a \emph{global} peak-normalized, peak-to-valley amplitude by analyzing archival ground based photometry spanning decades (\emph{c.f.} Section \ref{sec:archival_phot}).
+This strategy resembles that adopted by \citet{2017ApJ...851..116M}, which interpreted variations in Kepler Full-Frame Images as activity cycles.
+
+We measure sinusoidal amplitudes and spurious trends simultaneously with a phenomenological forward-modeling procedure that fits a sum of a sine wave and a polynomial of order $N_{\rm poly}$.
+We determine the period $P$ of the sine wave from the multiterm Lomb-Scargle periodogram \citep{ivezic14}.
+The linear model can then be solved analytically for the coefficients of the polynomial terms and the sine and cosine terms with linear least squares.
+For clarity, fitting a straight line trend equates to a first order polynomial, $N_{\rm poly}=1$:
+
+\begin{equation}
+\hat f = c_0 + c_1 \cdot t + c_2 \cdot \sin{\frac{2\pi t}{P}} + c_3 \cdot \cos{\frac{2\pi t}{P}}
+\end{equation}
+
+A simple sine wave may not faithfully capture more complex oscillatory behavior, like piecewide flat-topped or sawtooth patterns.
+We allow even more model flexibility by adding higher-order harmonic structures in a Fourier Series \citep{vanderplas15a} truncated to the first $N_{\rm Fourier}$ components:
+
+\begin{equation}
+  \begin{split}
+ \hat f  & =  \sum_{i=0}^{N_{\rm poly}} c_i \cdot t^i \\
+         & + \sum_{j=1}^{N_{\rm Fourier}} \Big( a_j \cdot \sin{\frac{2\pi j t}{P}} \\
+         & + b_j \cdot \cos{\frac{2\pi j t}{P}} \Big)
+\end{split}
+\end{equation}
+
+Our phenomenological forward model has a total of $N_{\rm poly}+2 \cdot N_{\rm Fourier}$ model parameters, representing the model complexity.
+We set these numbers $N_{\rm poly}, N_{\rm Fourier}$ through a cross-validation procedure that balances the bias-variance tradeoff.
+Once we have our model parameters in-hand, we overplot the observed lightcurve with a densely-sampled phenomenological model, examining the residuals for any additional noise structures, such as exoplanets or flares, which are masked and we iteratively re-compute the refined predicted flux time series.
+We discard the nonzero ($i>0$) polynomial terms, yielding a constant plus harmonic model, which is then peak-normalized and deemed the trend-free stellar lightcurve $\hat f_{\rm \star}(t)$.
+The detrended stellar amplitude is then: $$ A = 1 - \min{f_{\rm \star}(t)}$$
+
 \section{Observations}\label{sec:obs}
@@
 
-\subsection{Photometric monitoring}
+\subsection{Long-term ground-based photometric monitoring} \label{sec:archival_phot}
 
@@
 \end{figure*}
+
+\subsection{K2 photometric monitoring} \label{sec:K2_obs}
 

### 2018-09-18 document/ms.tex
Add prose about measurement philosophy and spectral method.  tick off some outline tasks.

@@
 In practice, additional factors complicate such a straightforward analysis.
-One main uncertainty is how to treat \emph{secular} trends, in which the star's flux waxes and wanes with both an oscillatory function of periods $P_{\rm rot}$ and with a slow-varying mean level with characteristic timescales $t_{\rm secular}$.
-Secular changes in flux could be interpreted as a growing or waning average starspot coverage fraction as in a long-term stellar activity cycles.
+One main uncertainty is how to treat \emph{secular} trends, in which the star's flux waxes and wanes with both an oscillatory function of periods $P_{\rm rot}$ and a slow-varying mean level with characteristic timescale $t_{\rm secular}$.
+Secular changes in flux could be interpreted as a growing or waning average starspot coverage fraction as in a long-term stellar activity cycle.
 The interpretation of secular trends depends on to-what-extent instrumental artifacts mimic these time-series structures.
@@
 The characteristic timescales of these instrumental biases tend to resemble the observing season- either campaigns for K2, or quarters for Kepler prime.
-Disk-free young stars exhibit bona fide secular trends of up to half a magnitude over periods of years-decades based on decades of ground-based photometric monitoring \citep{grankin08}.
+Meanwhile, disk-free young stars exhibit bona fide secular trends of up to half a magnitude over periods of years-decades based on decades of ground-based photometric monitoring \citep{grankin08}.
 
@@
 The detrended stellar amplitude is then: $$ A = 1 - \min{f_{\rm \star}(t)}$$
+
+\subsection{Two-temperature spectral inference framework}
+
+We employ the \texttt{Starfish}\footnote{Forked from the original (\href{https://github.com/iancze/Starfish}) at https://github.com/gully/Starfish} \citep{czekala15} spectral inference framework, as adapted from  by \citet{2017ApJ...836..200G}.
+The \texttt{Starfish} framework builds a forward-model of the observed spectrum based spectrally emulated pre-computed synthetic model grid spectra.
+We employed the PHOENIX synthetic model with an updated version of \texttt{Starfish} that maintains the native absolute fluxes from \citet{husser13}, rather than the inaccurate interpolation introduced in the Appendix of \citet{2017ApJ...836..200G}.
+
+The likelihood-based Bayesian inference framework \texttt{Starfish} is for evaluating the posterior probability of parameters given an observed spectrum, \emph{assuming the model is correct}.
+The model assumptions are:
+
+\begin{itemize}
+  \item Stellar photospheres are composed of exactly two distinct temperature components.
+  \item Most of the spectral lines arise from known stellar atmospheric physics \citep{husser13}.
+  \item The low temperature is above some finite threshold, typically $T>2400$ K.
+  \item The two components share the same surface gravity and metallicity.
+\end{itemize}
+
+The inference framework provides a \emph{measurement} of the temperatures and projected filling factor of the two components.
+The inference framework makes no effort to conduct \emph{model comparison}--- whether two temperature components are really needed over one, for example, or whether-or-not three components are warranted to capture additional, unexplained variance.
+Nor does the framework conduct \emph{detection} of starspots-- detection has usually already been established by the high precision photometric time series observations that reveal conspicuous undulations indicative of distinct surface structures with distinct emergent photospheres.
+We know the spots are there.
+We simply aim to quantify the first moment of their physical properties-- the average coverage fractions, and the characteristic temperatures.
 
@@
 We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra using the inference framework \texttt{Starfish} \citep{czekala15}, as extended by \citet{2017ApJ...836..200G}.
-We employed PHOENIX synthetic model with an updated version of \texttt{Starfish} that maintains the native absolute fluxes from \citet{husser13}, rather than the slightly inaccurate interpolation introduced in the Appendix of \citet{2017ApJ...836..200G}.
 We ran 5000 samples with 40 \texttt{emcee} walkers \citep{foreman13}, with manual spot-checking of convergence.

### 2018-10-09 document/ms.tex
Previously uncommitted prose-- writing in the ms.tex document

@@
 zero Kelvin) starspot near the equator of a modestly inclined star.
-Ignoring limb darkening, the peak-normalized, peak-to-valley amplitude of of the lightcurve is equal to the areal filling factor of the starspot.
+We refer to this scenario as the Simplest Possible Analytic Starspot Model (SPASM).
+Briefly, the SPASM interprets the lightcurve minimum as arising from a single, non-emitting, equatorial starspot on an edge-on star, and interprets the lightcurve maximum as \emph{spot-free}, that is, entirely devoid of starspots.
+With these admittedly extreme assumptions, the flux minimum $F_{min}$ of a peak-normalized lightcurve is exactly equal to the starspot areal surface coverage fraction, $f_{\mathrm{spot}}$, ignoring limb darkening.
 
@@
 
-The third illustration depicts another pathological geometry: the \emph{pole-on} star has a starspot that grows and shrinks cyclicly with a period $P \neq P_{\rm rot}$.
+%The third illustration depicts another pathological geometry: the \emph{pole-on} star has a starspot that grows and shrinks cyclicly with a period $P \neq P_{\rm rot}$.
 In this scenario, the rotation period is likely to be mis-identified.
@@
 
-The right-most illustration depicts a high-latitude active longitude in which the starspot is always visible from the observers perspective, but rotational modulation geometrically forshortens the perceived solid angle of the spot owing to projection effects, and limb darkening.
+%The right-most illustration depicts a high-latitude active longitude in which the starspot is always visible from the observers perspective, but rotational modulation geometrically forshortens the perceived solid angle of the spot owing to projection effects, and limb darkening.
 The amplitude of the lightcurve depends sensitively on the inclination of the star, the latitude of the spot, the wavelength-dependent limb darkening, the waveband of the observation, the temperature constrast of the spot, and the size of the spot.
@@
  \centering
- \includegraphics[width=0.98\textwidth, trim={0 5cm 0 4cm},clip]{figures/cartoon_illustration.pdf}
+ \includegraphics[width=0.58\textwidth, trim={0 5cm 16cm 4cm},clip]{figures/cartoon_illustration.pdf}
  \caption{Cartoon illustration of stars possessing different inclinations, starspot geometries, and positions, yet possessing the same lightcurve morphologies.}
@@
 
-\begin{equation}
+\begin{equation} \label{eqn:Fourier}
   \begin{split}
@@
 The inference framework provides a \emph{measurement} of the temperatures and projected filling factor of the two components.
-The inference framework makes no effort to conduct \emph{model comparison}--- whether two temperature components are really needed over one, for example, or whether-or-not three components are warranted to capture additional, unexplained variance.
-Nor does the framework conduct \emph{detection} of starspots-- detection has usually already been established by the high precision photometric time series observations that reveal conspicuous undulations indicative of distinct surface structures with distinct emergent photospheres.
-We know the spots are there.
-We simply aim to quantify the first moment of their physical properties-- the average coverage fractions, and the characteristic temperatures.
+The inference framework makes no effort to conduct \emph{model comparison}--- whether three components are warranted to capture additional, unexplained variance.
+Nor does the framework conduct \emph{detection} of starspots-- detection has already been established by the high precision photometric time series observations that reveal conspicuous undulations indicative of distinct surface structures with distinct emergent photospheres.
+Simply put, lightcurves detect spots, spectra measure the spot properties.
+Our measurement technique aims to quantify the \emph{first moment} in an ostensibly more complex distribution-- the average coverage fractions, and the characteristic temperatures.
 
@@
 We compiled many sources of publicly available $V-$band photometry datapoints including 236 from \citep{grankin08}, 552 from ASAS3 \citep{pojmanski04}, 473 from the AAVSO archive \citep{kafka16}, and 306 unpublished data points from the ASAS-SN survey \citep{shappee14}.
-We spot-checked the diverse sources of photometry finding consistency in estimated flux levels when acquired near-contemporaneously.Figure \ref{fig:PhotTime} shows the compilation of all available photometry on V827 Tau.
+We spot-checked the diverse sources of photometry finding consistency in estimated flux levels when acquired near-contemporaneously.
+Figure \ref{fig:PhotTime} shows the compilation of all available photometry on V827 Tau.
 Figure \ref{fig:PhotStamps} shows a zoom-in postage stamp on each season, phase folded with a period $P=3.75837$ days.
@@
 %Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and Fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.
- We performed a multiterm Lomb-Scargle periodogram \citep{ivezic14}, and Fourier series truncated to the first $\sim 4$ components \citep{vanderplas15a} on the K2 C13 lightcurve, yielding a 3.7584 day period.
-We then fit a second order polynomial plus sine-and-cosine model with linear least squares.
+ We performed a multiterm Lomb-Scargle periodogram \citep{ivezic14} truncated to the first $\sim 4$ components \citep{vanderplas15a} on the K2 C13 lightcurve, yielding a 3.7584 day period.
+We then fit a second order polynomial plus sine-and-cosine model (\emph{c.f} Eq.
+\ref{eqn:Fourier}) with linear least squares.
 The periodic minimum K2 flux corresponds to a flux decrement of 23.5\% from its maximum.
@@
 
-We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra using the inference framework \texttt{Starfish} \citep{czekala15}, as extended by \citet{2017ApJ...836..200G}.
+We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra applying \texttt{Starfish} separately for each spectral order.
 We ran 5000 samples with 40 \texttt{emcee} walkers \citep{foreman13}, with manual spot-checking of convergence.
@@
 
-We observed reasonably good agreedment when we overplotted our model prediction spectra with the data.
+We observed reasonably good agreement when we overplotted our model prediction spectra with the data.
 We do not expect the models to be perfect, due to known model mis-specifications such as imperfect line lists and un-modeled magnetic Zeeman broadening, to name a few.
+Figure \ref{fig:IGRINS-spectra} shows observed IGRINS spectra with a single draw from the probabilistic spectral decompositions from Starfish.
+The probabilistic nature of the decomposition method means that a range of filling factors and hot-and-cool temperatures are consistent with the data.
+The suite of conceivable spectral decompositions is not shown for clarity-- we do not prescribe that the decompositions shown represent the ``best fit'' or ``optimal'' ones, simply a draw with a ``middle-of-the-road'' filling factor estimate.
+The emcee-adapted Starfish framework samples each spectral order independently, and therefore allows each order to have its own, potentially discordant posterior for each chunk of spectrum.
+Any single spectral order's parameters may ostensibly seem in discord with an adjacent spectral order.
+In practice, the probabilistic spread of filling factors and temperatures usually means that there exists some combination of parameters that is consistent with almost all of the spectral orders.
 
-The archival and K2 lightcurves constrain the minimum possible starspot coverage, assuming the Simplest Possible Analytic Starspot Model (SPASM).
-Briefly, the SPASM interprets the lightcurve minimum as arising from a single, non-emitting, equatorial starspot on an edge-on star, and interprets the lightcurve maximum as \emph{spot-free}, that is, entirely devoid of starspots.
-With these admittedly extreme assumptions, the flux minimum $F_{min}$ is exactly equal to the starspot areal surface coverage fraction, $f_{\mathrm{spot}}$.
+Some outlier spectral orders exhibit posterior clusters far away from any of the other spectral orders.
+These outlier spectral orders may stem from either poor synthetic spectral models, violated assumptions, or bona-fide detections of probing deeper into the photosphere due (ref Berdyugina 20xx).
+
+\begin{figure*}
+\centering
+\includegraphics[width=0.98\textwidth]{figures/H_band_spectra_3x6.pdf}
+\caption{Observed IGRINS spectra (thick stepped gray line) for 15 spectral orders $m$,  overplotted with a composite spectrum (thin purple line) composed from Starfish-derived stellar posterior parameters; the shown parameters possess the median filling factor of the burned-in MCMC samples.
+The faint dotted blue line shows the hot $T_h$ photospheric component of the spectral decomposition, while the thick red line shows the cool $T_c$ component.
+The sum of the red and blue lines is the purple line.
+\label{fig:IGRINS-spectra}}
+\end{figure*}
+
+The archival and K2 lightcurves constrain the minimum possible starspot coverage as described in the Methods Section.
 The SPASM can be applied to a single season, such that there always exists a spot-free hemisphere, or can be applied to a global, long-term photometric dataset such as the one we have assembled for V827 Tau.
@@
 
-Figure \ref{} plots the constraints of starspot filling factor versus starspot temperature.
-The burned-in MCMC draws from the posterior probability density distribution inferred from IGRINS spectra aggregated for all spectral orders are overplotted as a 2D-histogram.
+Figure \ref{} plots the constraints of starspot filling factor versus starspot temperature.  The median and $5^{th}$ and $95^th$ percentiles of the MCMC samples are shown.
 

### 2018-10-09 document/ms.tex
Prose about K2 observations and analysis, Gaia DR2, kinematics, and update outline to include high resolution imaging companion searches

@@
 
-We employ the \texttt{Starfish}\footnote{Forked from the original (\href{https://github.com/iancze/Starfish}) at https://github.com/gully/Starfish} \citep{czekala15} spectral inference framework, as adapted from  by \citet{2017ApJ...836..200G}.
+We employ the \texttt{Starfish}\footnote{Forked from the original \url{https://github.com/iancze/Starfish} at \url{https://github.com/gully/Starfish}} \citep{czekala15} spectral inference framework, as adapted from  by \citet{2017ApJ...836..200G}.
 The \texttt{Starfish} framework builds a forward-model of the observed spectrum based spectrally emulated pre-computed synthetic model grid spectra.
@@
 
-We retrieved K2 Campaign 13 (C13) \cite{2014PASP..126..398H} lightcurves for V827 Tau, possessing EPIC ID 210698281.
+We retrieved the K2 Campaign 13 (C13) \cite{2014PASP..126..398H} long cadence (30 minute cadence) Target Pixel File for EPIC ID 210698281 (V827 Tau) from the Mikulksi Archive for Space Telescopes (MAST).
+Observations of this target were requested in 9 distinct Guest Observer proposals: GO13117 (PI Cody), GO13123 (PI Stello), GO13009 (PI Rizzuto), GO13016 (PI Gaidos), GO13002 (PI Prsa), GO13086 (PI Boyd), GO13119 (PI Johns-Krull), GO13070 (PI Plachy), GO13118 (PI Stringfellow).
+Proposal GO13070 selected this target based on its appearance as a Cepheid variable star, possibly based on its unusually large amplitude of photometric variability.
+
+\subsection{Gaia DR2 and kinematics} \label{sec:GaiaDR2}
+
+V827 Tau appears in Gaia DR2 \citep{2016A&A...595A...1G, 2018A&A...616A...1G} as source 3314338163954491136, with a parallax of $6.1432 \pm 0.351 $ milliarcseconds, and proper motions in RA and dec of $9.55 \pm 0.72, -13.406 \pm 0.473$ respectively.
+Individual photometric epochs were not available for this star.
+\citet{nguyen12} report a radial velocity (RV) of V827 Tau of $17.77 \pm 0.05 (stat) \pm 1.9 (sys) $ km/s based on four measurement epochs with the Magellan Inamori Kyocera Echelle (MIKE, \citet{2003SPIE.4841.1694B}).
+
+\subsection{High Spatial Resolution Imaging} \label{sec:imaging}
+We spot-checked a few sources of high-spatial resolution imaging to probe the prospect of binarity for V827 Tau.
 
@@
 %Multiterm Lomb-Scargle periodograms \citep{ivezic14}, and Fourier series truncated to the first $\sim 4$ components]{vanderplas15a}.
- We performed a multiterm Lomb-Scargle periodogram \citep{ivezic14} truncated to the first $\sim 4$ components \citep{vanderplas15a} on the K2 C13 lightcurve, yielding a 3.7584 day period.
+
+\subsection{Kinematics and cluster membership}
+The GaiaDR2 positional and MIKE RV data provide constraints on membership to the Taurus cluster.
+We computed the probability of membership to the field and the Taurus star forming region using the Banyan $\Sigma$ probabilistic cluster membership framework \footnote{Banyan $\Sigma$: webtool \url{http://www.exoplanetes.umontreal.ca/banyan/banyansigma.php}, with source code at \url{https://github.com/jgagneastro/banyan_sigma}} \citep{2018ApJ...856...23G}.
+We found an $84.1\%$ probability of Taurus membership, and a $15.9\%$ chance of field membership.
+
+\subsection{K2 data analysis}
+We assembled the K2 C13 lightcurve using the \texttt{lightkurve} package\footnote{\url{http://lightkurve.keplerscience.org/}}.
+We computed custom simple aperture photometry using all telemetered pixels in the postage stamp window.
+This generous aperture choice reduces motion-induced systematic trends attributable to flux spilling outside of the pre-defined Kepler pipeline aperture.
+No custom background subbtraction was applied.
+
+We performed a multiterm Lomb-Scargle periodogram \citep{ivezic14} truncated to the first $4$ components \citep{vanderplas15a} on the K2 C13 lightcurve, yielding a 3.7584 day period, deemed the rotation period of the star.
+Parenthetically, a unique rotation period is ill-defined in the presence of differential rotation, so instead we think of this number as the rotation rate evaluated at the---unknown, possibly dynamic---latitude of the dominant spot or spot group.
 We then fit a second order polynomial plus sine-and-cosine model (\emph{c.f} Eq.
@@
 
+This work has made use of data from the European Space Agency (ESA) mission
+{\it Gaia} (\url{https://www.cosmos.esa.int/gaia}), processed by the {\it Gaia}
+Data Processing and Analysis Consortium (DPAC,
+\url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}). Funding for the DPAC
+has been provided by national institutions, in particular the institutions
+participating in the {\it Gaia} Multilateral Agreement.
+
 {\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}, \facility{Gaia}

### 2019-01-18 document/ms.tex
Some new text on a Friday afternoon, trying to decide whether this is V827 Tau only or all Grankin 08 WTTS with K2 available

@@
 %\documentclass[iop,revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to twocolumn for manuscript
-\documentclass[twocolumn]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
+\documentclass[revtex4]{emulateapj}% change onecolumn to iop for fancy, iop to onecolumn for manuscript
 %\documentclass[12pt,preprint]{aastex}
@@
 
-\shorttitle{Extreme Starspots in Taurus}
+\shorttitle{V827 Tau starspots with K2 and IGRINS}
 
@@
 
-\title{The coverage fraction of starspots on young Taurus members and consequences for stellar ages estimates at 1$-$10 Myr}
+\title{The coverage fraction of starspots on V827 Tau and consequences for stellar ages estimates at 1$-$10 Myr}
 
@@
 
-We assess starspot temperatures and coverage fraction for three heavily spotted Taurus pre-main sequence young stellar objects from their high-resolution, high bandwidth near infrared IGRINS spectroscopy.
+We assess starspot temperatures and coverage fraction for V827 Tau---a heavily spotted Taurus pre-main sequence young stellar object---based on its high-resolution, high bandwidth near infrared IGRINS spectroscopy.
 We forward model the spectra with a mixture of cool and hot photosphere components using the \texttt{Starfish} spectral inference framework.
-The disk-free, non-accreting sample members have 10$-$30 years worth of polychomatic photometry, which we use in four ways: first, to register the acquisition time of the spectroscopic measurement to the stellar rotational phase; second, to derive the secular changes of areal coverage fraction over 1 to 30 year timescales; third, to derive rotation periods; and fourth, to assign lower-limits to areal filling factors based on the amplitude of photometric variation and limiting case of non-emitting equatorial spots.
-We derive starspot temperatures in the range of $x$ to $y$ K, and filling factors of $v$ to $z$.
-These filling factors are typically $k$ to $m$ times higher than the limiting case of non-emitting equatorial spots, implying that either the stars possess large circumpolar starspots with the stellar spin axis inclined moderately towards our reference frame, or that the stars possess three or more dominant temperature components, rendering our two-temperature retrieval process flawed.
-The filling factors and temperatures cause effective temperature estimates to systematically decrease, confounding age and mass estimates of these young stars and by extension all previous spectral-type-based estimates of fundamental properties of heavily spotted stars, though more work is needed.
+The disk-free, non-accreting V827 Tau has 30 years worth of polychomatic photometry, including Kepler/K2, ASASSN, and the ROTOR program.
+We use the photometry in four ways: first, to register the acquisition time of the spectroscopic measurement to the stellar rotational phase; second, to derive the secular changes of areal coverage fraction over 1 to 30 year timescales; third, to derive rotation periods; and fourth, to assign lower-limits to areal filling factors based on the amplitude of photometric variation and limiting case of non-emitting equatorial spots.
+We derive starspot temperatures $<3000$ K, compared to a 4100 K ambient photosphere, with filling factors of $60$ to $80\%$.
+These filling factors are $\sim3$ times large than the limiting case of a solitary non-emitting equatorial spot, implying that the stars either possess longitudinal symmetries in the starspots surface distribution, and/or high latitude starspots moderately inclined towards the observer.
+The filling factor and temperature cause effective temperature estimates to systematically decrease, confounding age and mass estimates of these young stars and by extension all previous spectral-type-based estimates of fundamental properties of heavily spotted stars, though more work is needed.
 The observations of secularly varying photometric amplitudes are consistent with the physical interpretations that some or all young stars pass through short-lived phases of enhanced starspot coverage, or that starspots migrate from near the poles towards the equator over time.
@@
 We first emphasize possible geometric degeneracies that can give rise to larger-than-expected starspots.
-We then collate numerous photometric and spectroscopic data sources (Section XXX), and their starspot-centric analyses (Section XXX).
-We combine inferences on our small sample of stars to assess the effect of starspots on the pre-main sequence HR-diagram (Section XXX).
-Finally we question our initial assumptions in Section XXX.
+We then collate numerous photometric and spectroscopic data sources (Section \ref{sec:obs}), and their starspot-centric analyses (Section \ref{sec:Analysis}).
+We combine inferences on our small sample of stars to assess the effect of starspots on the pre-main sequence HR-diagram (Section \ref{sec:Analysis}), and finally we revisit and question the assumptions of our analysis.
 
@@
 
+\subsection{Spectral inference}
 We derived starspot temperatures and areal filling factors from IGRINS $H-$band spectra applying \texttt{Starfish} separately for each spectral order.
@@
 The probabilistic nature of the decomposition method means that a range of filling factors and hot-and-cool temperatures are consistent with the data.
-The suite of conceivable spectral decompositions is not shown for clarity-- we do not prescribe that the decompositions shown represent the ``best fit'' or ``optimal'' ones, simply a draw with a ``middle-of-the-road'' filling factor estimate.
+The suite of conceivable spectral decompositions is not shown for clarity-- we do not prescribe that the decompositions shown represent the ``best fit'' or ``optimal'' ones, simply a draw with a probable filling factor estimate.
 The emcee-adapted Starfish framework samples each spectral order independently, and therefore allows each order to have its own, potentially discordant posterior for each chunk of spectrum.
@@
 Some outlier spectral orders exhibit posterior clusters far away from any of the other spectral orders.
-These outlier spectral orders may stem from either poor synthetic spectral models, violated assumptions, or bona-fide detections of probing deeper into the photosphere due (ref Berdyugina 20xx).
+These outlier spectral orders may stem from either poor synthetic spectral models, violated assumptions, or bona-fide detections of probing to deeper into the photosphere and perceiving a smaller cross-section of spots than on the surface (M.
+Panja, priv.
+comm.).
 
@@
 
-Figure \ref{} plots the constraints of starspot filling factor versus starspot temperature.  The median and $5^{th}$ and $95^th$ percentiles of the MCMC samples are shown.
+Figure \ref{fig:V827TauStarfish} plots the constraints of starspot filling factor versus starspot temperature.  The median and $5^{th}$ and $95^th$ percentiles of the MCMC samples are shown.
 
@@
 \centering
-  \includegraphics[width=0.98\textwidth]{figures/V827_Tau_Starfish_results.pdf}
+  \includegraphics[width=0.5\textwidth]{figures/V827_Tau_Starfish_results.pdf}
   \caption{Results of Starfish-based inference of starspot filling factor and temperature for 22 IGRINS $H-$band orders.
@@
 \end{figure*}
+
+\section{Discussion}\label{sec:discussion}
+
+\emph{text}
 
@@
 
-\appendix
-
-\section{Are starspots confusing?}
-\label{methods-details}
-
-Short answer: no!
-
 \acknowledgements
@@
 %ADS
-We thank ADS!
+This work used the Immersion Grating Infrared Spectrograph (IGRINS) that was developed under a collaboration between the University of Texas at Austin and the Korea Astronomy and Space Science Institute (KASI) with the financial support of the US National Science Foundation under grant AST-1229522, of the University of Texas at Austin, and of the Korean GMT Project of KASI.
+This research has made use of NASA's Astrophysics Data System.
 
-%Kepler
 This paper includes data collected by the Kepler mission. Funding for the Kepler mission is provided by the NASA Science Mission directorate.
 
-% MAST
-Some/all of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
+Some of the data presented in this paper were obtained from the Mikulski Archive for Space Telescopes (MAST).
 STScI is operated by the Association of Universities for Research in Astronomy, Inc., under NASA contract NAS5-26555.
+
+We acknowledge with thanks the variable star observations from the AAVSO International Database contributed by observers worldwide and used in this research.
 
@@
 
-{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{ARC (TripleSpec)}, \facility{Hale (DBSP)}, \facility{Gaia}
+{\it Facilities:} \facility{Smith (IGRINS)}, \facility{AAVSO}, \facility{CFHT (ESPaDOnS)}, \facility{INTEGRAL (OMC)}, \facility{ASAS}, \facility{CrAO:1.25m}, \facility{Gaia}
 

### 2019-01-19 code/plot_specific_mix_model.py
Add some hack to the plotting code to compute the flux ratios of two Phoenix spectra in the K2 passband

@@ -15,6 +15,7 @@ parser.add_argument("--config", action='store_true', help="Use config file inste
 parser.add_argument("--static", action="store_true", help="Make a static figure of one draw")
 parser.add_argument("--animate", action="store_true", help="Make an animation of many draws from the two components.")
 parser.add_argument("--OG", action="store_true", help="The Original Gangster version, clunky and all.")
+parser.add_argument("--blitz", action="store_true", help="Take flux ratios of temps.")
 args = parser.parse_args()
 
 import os
@@ -206,7 +207,7 @@ def lnprob_all(p):
 
 draws = []
 
-if not args.config:
+if not (args.config or args.blitz):
     try:
         ws = np.load("emcee_chain.npy")
         burned = ws[:, -200:,:]
@@ -316,6 +317,44 @@ if args.config:
     df_out['model_hot50'] = lnprob_all(pset2)
 
     df_out.to_csv('spec_config.csv', index=False)
+
+# Compute the flux ratios for all temp combos
+if args.blitz:
+
+    kep_response = pd.read_csv(os.path.expandvars('$xveganx/data/K2/kepler_response_hires1.txt'),
+                           names=['wl_nm','trans'],
+                           skiprows=9, delim_whitespace=True)
+    kep_response['wl_ang'] = kep_response.wl_nm * 10.0
+    kep_response = kep_response[(kep_response.wl_ang > 4200) & (kep_response.wl_ang < 9200)]
+    kep_response['trans_norm'] = kep_response.trans / np.sum(kep_response.trans)
+    kep_response = kep_response.reset_index(drop=True)
+
+    df_out = pd.DataFrame()
+
+    with open('s0_o0phi.json') as f:
+        s0phi = json.load(f)
+
+    for T_spot in np.arange(2700, 3901, 50):
+
+        psl = (Starfish.config['Theta']['grid']+
+          [Starfish.config['Theta'][key] for key in ['vz', 'vsini', 'logOmega', 'teff2', 'logOmega2']] +
+          s0phi['cheb'] +
+          [s0phi['sigAmp']] + [s0phi['logAmp']] + [s0phi['l']])
+
+        ps = np.array(psl)
+        ps[6] = T_spot
+
+        pset1 = ps.copy()
+        pset1[5] = -20
+        model_cool = lnprob_all(pset1)
+        pset2 = ps.copy()
+        pset2[7] = -20
+        model_hot = lnprob_all(pset2)
[…]

### 2019-01-19 code/star_base.py

@@ -11,7 +11,7 @@ from scipy.special import j1
 from scipy.interpolate import InterpolatedUnivariateSpline
 from scipy.linalg import cho_factor, cho_solve
 from numpy.linalg import slogdet
-from astropy.analytic_functions import blackbody_lambda
+#from astropy.analytic_functions import blackbody_lambda
 from astropy import units as u
 import logging
 

### 2019-01-19 code/xphotometryx.py

@@ -218,6 +218,7 @@ def plot_season_postage_stamps(master, season_agg, epochs, ylim=(13.7, 13.3), sa
     for i in range(n_seasons):
         # get the data and best-fit angular frequency
         s = season_agg.season[i]
+        print(s)
         ids = master.season == s
         df = master[ids]
         t = df.JD_like.values
@@ -236,11 +237,14 @@ def plot_season_postage_stamps(master, season_agg, epochs, ylim=(13.7, 13.3), sa
             reg = 0.3 * np.ones(2 * Nterms + 1)
             reg[:3] = 0 # no regularization on low-order terms
 
-        modelV = LombScargle(Nterms=4, regularization=reg)
-        mask = y == y # We can mask flares later on
-        modelV.fit(t[mask], y[mask], dy[mask])
         tfit = np.linspace(0, this_P, 100)
-        yfitV = modelV.predict(tfit, period=this_P)
+        try:
+            modelV = LombScargle(Nterms=4, regularization=reg)
+            mask = y == y # We can mask flares later on
+            modelV.fit(t[mask], y[mask], dy[mask])
+            yfitV = modelV.predict(tfit, period=this_P)
+        except:
+            yfitV = np.nanmedian(y)*np.ones(len(tfit))
 
 
         # plot the phased data
